ASR-Output-Correcting Webapp After 6 Years

### 2018-03-24 2018-tsd-brno/webapp.tex
s/transcribing software/transcription software/

\subsection{Transcribing apps}

The main differences to common transcribing software are that

@@

We can still learn a lot from transcribing software. The ease of performing
common tasks, like pausing, resuming and rewinding is crucial for the user
experience and in effect for the amount of submissions that we receive. Also,
the way the text is displayed synchronously to the audio played has a big impact
and the approaches have a lot of space for variation.

@@

Most transcribing programs show the transcription as a vertical list of
utterances, see Figure~\ref{fig:transcriber1} for an example of
{\em{Transcriber}}\footnote{trans.sourceforge.net}, a veteran open-source
transcription tool. We attribute this to the fact that the atomic elements of
the transcription are the user-entered utterances and their boundaries are
reliable. In our case, the atomic elements are words. There are sentences, sure,
but the segmentation to sentences by the ASR is very unreliable, so we want it
to be natural to transcribe a segment overlapping sentence boundaries.

>>>>

\subsection{Transcription apps}

The main differences to common transcription software are that

@@

We can still learn a lot from transcription software. The ease of performing
common tasks, like pausing, resuming and rewinding is crucial for the user
experience and in effect for the amount of submissions that we receive. Also,
the way the text is displayed synchronously to the audio played has a big impact
and the approaches have a lot of space for variation.

@@

Most transcription programs show the transcription as a vertical list of
utterances, see Figure~\ref{fig:transcriber1} for an example of
{\em{Transcriber}}\footnote{trans.sourceforge.net}, a veteran open-source
transcription tool. We attribute this to the fact that the atomic elements of
the transcription are the user-entered utterances and their boundaries are
reliable. In our case, the atomic elements are words. There are sentences, sure,
but the segmentation to sentences by the ASR is very unreliable, so we want it
to be natural to transcribe a segment overlapping sentence boundaries.
